Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-09-08 grove-paper.tex
Figure out examples to use for multi-user cycles and disconnection
Rough out last figures in section 2

TODO: alice and bob

@@

\subsubsection{Cycles}
\label{sub:Cycles}

@@

@@

\begin{figure}
\centering

TOP: *(*(1, \hole), *(2, \hole))

LEFT: *(*(1, *(2, \hole)), \hole)

RIGHT: *(\hole, *(2, *(1, \hole)))

BOTTOM: *(\hole, \hole) *(1, *(2, \#1))

\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure}

@@

>>>>

@@

\subsubsection{Single-User Cycles}
\label{sub:Cycles}

@@

\subsubsection{Multi-User Cycles}
\label{sub:Multi-User Cycles}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{+}_{4}$" [> "left", > "19"'],
    "$\texttt{*}_{6}$" [> "left", > "19"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
   },
   {
    "$\texttt{+}_{4}$" [> "left", > "19"'] -> {
     "$\texttt{*}_{6}$" [> "left", > "19"']
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
   },
   {
    "$\texttt{*}_{6}$" [> "left", > "19"'] -> {
     "$\texttt{+}_{4}$" [> "left", > "19"']
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
   },
   {
    v1/"$\texttt{*}_{6}$" [> "left", > "19"'],
    v2/"$\texttt{+}_{4}$" [> "left", > "19"']
   }
  }
 }
};
\path[draw] (v1) -> (v2);
\path[draw] (v2) -> (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure}

@@

\subsection{Disconnection}
\label{sub:Disconnection}

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{1}_{4}$" [> "left", > "19"'],
   },
   "$\texttt{+}_{6}$" [> "left", > "19"'] -> {
    "$\texttt{2}_{4}$" [> "left", > "19"'],
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{1}_{4}$" [> "left", > "19"'],
    "$\texttt{+}_{6}$" [> "left", > "19"'] -> {
     "$\texttt{2}_{4}$" [> "left", > "19"'],
    }
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{+}_{6}$" [> "left", > "19"'] -> {
    "$\texttt{2}_{4}$" [> "left", > "19"'],
    "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
     "$\texttt{1}_{4}$" [> "left", > "19"'],
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"']
 }
};
\path (-1cm,-2cm) graph[graph style] {
 "$\texttt{+}_{6}$" [> "left", > "19"'] -> {
  "$\texttt{2}_{4}$" [> "left", > "19"'],
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
  "$\texttt{1}_{4}$" [> "left", > "19"'],
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Disconnection}
\label{fig:Disconnection}
\end{figure}
